---
title: "DBP stats for `r params$name`"
output:
  pdf_document: default
  html_document: default
params:
  name: dbp_sim_data_20190226
editor_options:
  chunk_output_type: console
header-includes:
  - \usepackage{draftwatermark}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(scales)
library(lemon)
library(knitr)
library(lubridate)
library(REdaS)
theme_set(theme_light())
source("R/dbp_stat_functions.R")
knitr::opts_chunk$set(fig.width=6, fig.height=4) 
```

```{r lens, include = FALSE}
lens <- read_delim(str_c("data/",params$name, ".csv"), delim = ";",
                   col_types = cols(
                                  .default = col_double(),
                                  JOB = col_character(),
                                  EYE = col_character(),
                                  TIMESTAMP = col_character(),
                                  LMRDONE = col_logical(),
                                  LMTDONE = col_logical(),
                                  POLAR = col_logical(),
                                  TINT = col_character(),
                                  LTYPE = col_character(),
                                  LDVEN = col_character(),
                                  LNAME = col_character(),
                                  ENGLOC = col_character(),
                                  POS34VALID = col_logical(),
                                  POSPEVALID = col_logical(),
                                  DBPVALID = col_logical(),
                                  LMERRMSG = col_character()
                                  )
) %>% 
    mutate(
        TOLVPRVH = get_tolvprvh(LDDRSPH, LDDRCYL),
        TOLVPRVV = get_tolvprvv(LDDRSPH, LDDRCYL),
        TIMESTAMP = ymd_hms(TIMESTAMP),
        POSPEID = factor(POSPEID),
        POSPEID = fct_recode(POSPEID, 
                             AutoPosPE = "0", 
                             SquareNotFound = "20060", 
                             EyeNotFound  = "20217",
                             BadEye = "20210",
                             InvalidMode = "20202"
                             ),
        LMERRCODE = as.factor(LMERRCODE),
        LMERRCODE = fct_recode(LMERRCODE, 
                                NoError = "0",
                                NoError = "21273",
                                NoError = "21315",
                                PatternError = "21013",
                                PatternError = "21223",
                                ProtectedMemoryError = "20899",
                                TransmissionError = "21246"
                                )
        ) %>%
    mutate(
       fcocx = FCOCIN * ((EYE=="R")-(EYE=="L")),
       fcocy = FCOCUP,
       PrpDeltaX = POSPEX + TPERRPEX + fcocx - (POS34X + TPERR34X),
       PrpDeltaY = POSPEY + TPERRPEY + fcocy - (POS34Y + TPERR34Y),
       PrpDeltaT = ((POSPET + TPERRPET)-(POS34T+TPERR34T)) -90*(EYE=="R")-270*(EYE=="L"),
       PrpDeltaT = ifelse(PrpDeltaT > 180, PrpDeltaT-360, PrpDeltaT),
       PrpDeltaT = ifelse(PrpDeltaT < -180, PrpDeltaT+360, PrpDeltaT)
       ) %>% 
    mutate(
        LDDRSEQ = LDDRSPH + LDDRCYL/2
        # LDDRCYL = abs(LDDRCYL)
        ) %>% 
    mutate(
        INSPRVH_DBP = extrapolate_prvh(INSPRVH, INSPRVV, INSPRSPH, INSPRCYL, INSPRAX,
                                        -DBPX, -DBPY, -DBPT),
        INSPRVV_DBP = extrapolate_prvv(INSPRVH, INSPRVV, INSPRSPH, INSPRCYL, INSPRAX,
                                        -DBPX, -DBPY, -DBPT),
        REL_DPRVH = (INSPRVH-LDPRVH)/TOLVPRVH,
        REL_DPRVV = (INSPRVV-LDPRVV)/TOLVPRVV,
        REL_DPRVH_DBP = (INSPRVH_DBP - LDPRVH)/TOLVPRVH,
        REL_DPRVV_DBP = (INSPRVV_DBP - LDPRVV)/TOLVPRVV
        )
```

## 1. Data processing and lens statistics

```{r lens_pr}
lens_pr <- lens %>% 
    filter(
        !(LMTDONE == FALSE & LMRDONE == FALSE & LMERRCODE == "NoError"),
        str_detect(LTYPE, "PR FF"),
        POS34VALID == TRUE,
        POS34MANU == FALSE,
        is.na(INSADD) == FALSE & is.nan(INSADD) == FALSE,
        POSPEID != "InvalidMode"
        )
```

The applied filter selects the rows that are compliant with the following conditions :

* LTYPE includes PR FF
* !(DLM.ReflectionResults.Done == FALSE && DLM.TResults == FALSE && DLM.LMERRCODE ==  0)
* POS34VALID == TRUE & POS34MANU == FALSE (automatic detection of the 34mm engravings)
* is.na(INSADD) == FALSE & is.nan(INSADD) == FALSE (valid measurement at Foco)
* POSPEID != "InvalidMode" (error when PPOS is in invalid mode, happens only in A&R mode - very rare)

The total number of lenses included is : `r lens_pr %>% nrow`.

Some basic statistics about the power, cylinder and addition :

```{r lens statistics}
lens_pr %>% 
    select(LDDRSEQ, LDDRCYL, LDADD) %>% 
    gather(NAME, VALUE) %>% 
    mutate(NAME = factor(NAME, levels = c("LDDRSEQ", "LDDRCYL", "LDADD"))) %>% 
    ggplot(aes(VALUE)) +
    geom_histogram(bins = 20, aes(fill = NAME), color = "black", alpha = 1) +
    facet_wrap(~ NAME, scales = "free")+
    guides(fill = FALSE)+
    labs(
        x = "[D]",
        y = "",
        title = ""
    )
    
```


## 2. Preliminary engravings detection and position 

### 2.1 Filter lenses with 180° errors on the 34mm engravings

```{r}
lens_pr %>% 
    mutate(ENG34_180_ERROR = INSADD < 0) %>% 
    count(ENG34_180_ERROR) %>% 
    mutate(per = n/sum(n)*100) %>% 
    kable(digits = 2)
```


Let's remove these 5 lenses from the dataset.

### 2.2 Detect lenses with automatic PE detection bu wrong PE x-y location

```{r}
lens_pr <- lens_pr %>% 
    mutate(
         POSPEID_char = POSPEID %>% as.character(),
         POSPEID_char = ifelse(
             as.character(POSPEID_char) == "AutoPosPE" & (abs(PrpDeltaX) > 2 | abs(PrpDeltaY) > 2),
             "AutoPosPE_WrongXY", 
             POSPEID_char
             ),
         POSPEID_char = ifelse(
             as.character(POSPEID_char) == "AutoPosPE" & abs(round(PrpDeltaT)) == 180 ,
             "AutoPosPE_180Err", 
             POSPEID_char),
         POSPEID = as.factor(POSPEID_char)
         )
```

```{r}
lens_pr %>% 
    count(POSPEID) %>% 
    mutate(
        POSPEID = fct_reorder(POSPEID, n),
        percents = n/sum(n),
        labely = percents + 0.07,
        labelt = percent(percents, accuracy = 0.01)
        ) %>% 
    ggplot(aes(POSPEID, percents, fill = POSPEID)) +
    geom_bar(stat =  "identity", color = "black") +
    geom_text(aes(y = labely, label = labelt)) +
    scale_y_continuous(labels = percent, limits = c(0, 1.1), breaks = seq(0, 1, by = 0.2))+
    labs(
        title = "PE detection performance",
        y = "",
        x = ""
        )+
    guides(fill=FALSE)+
    coord_flip()
```

### 2.2 Preliminary engraving position vs. expected


Here the comparison of the position of the PRP based on the engravings at 34mm
and the PRP based on the preliminary engravings. Only the lenses with auto-positioning
for both pairs of engravings and no 180° error are considered.


```{r lens_auto}
lens_pe_auto <- lens_pr %>% 
   filter(
       POSPEID == "AutoPosPE",
       POS34MANU == FALSE
       )
```


```{r PrpDelta_plot}

lens_pe_auto %>% 
    select(PrpDeltaX, PrpDeltaY, PrpDeltaT) %>% 
    gather(Name, Value) %>% 
    mutate(Name = factor(Name, levels = c("PrpDeltaX", "PrpDeltaY", "PrpDeltaT"))) %>% 
    ggplot(aes(Value))+
    geom_histogram(bins = 40, color = "black", aes(fill = Name), alpha = 1) +
    scale_x_symmetric(lim = c(-1.,1.))+
    guides(fill = FALSE)+
    facet_wrap(~ Name) +
    labs(
        x = "",
        y = "",
        title = "Discrepencies between PE and 34mm engravings"
    )
```


#### Distribution averages

```{r}
lens_pe_auto %>% 
    select(PrpDeltaX, PrpDeltaY, PrpDeltaT) %>% 
    summarize_all(median) %>% 
    kable(digits = 2)
```

## 3. DLM and DBP success rate and output

### 3.1 DLM Error statistics

Here is the distribution of the DLM errors for the filtered lenses.
Note that a GNG error or GNG not tested is considered as no error here.

```{r}

lens_pr %>% 
    count(LMERRCODE) %>% 
    mutate(
        LMERRCODE = fct_reorder(LMERRCODE, n),
        percents = n/sum(n),
        labely = percents + 0.07,
        labelt = percent(percents, accuracy = 0.01)
        ) %>% 
    ggplot(aes(LMERRCODE, percents, fill = LMERRCODE)) +
    geom_bar(stat =  "identity", color = "black") +
    geom_text(aes(y = labely, label = labelt)) +
    scale_y_continuous(labels = percent, limits = c(0, 1.1), breaks = seq(0, 1, by = 0.2))+
    labs(
        title = "LM error codes",
        y = "",
        x = ""
        )+
    guides(fill=FALSE)+
    coord_flip()

```

#### More info for the PatternError

```{r}
lens_pr %>% 
    mutate(
        HASPNE = (LMERRCODE == "PatternError"),
        LIND = round(LIND, digits = 2),
        LIND = as.factor(LIND)
        ) %>% 
    group_by(LIND) %>% 
    summarize(
        HASPNE_pct = mean(HASPNE)
    ) %>% 
    ggplot(aes(LIND, HASPNE_pct, fill = LIND)) +
    geom_col()+
    scale_y_continuous(labels = percent)+
    guides(fill = FALSE) +
    labs(
        title = "Percentages of PatternError per LIND",
        x = "LIND",
        y = ""
    )
```

### 3.2 DBP success rate

Among the lenses without an error at the DLM , here is the percentage of successful DBP processing.

First let's remove the lenses with a INSAV value greater than 0.5 (in absolute value), a GMC greater than 1 or a ERRCYLV error greater than 0.5.

```{r lens_auto_dbp_nv}
lens_pr_noerr <- lens_pr %>% 
    filter(LMERRCODE == "NoError") %>% 
    mutate(
        ERRDRSEQ = INSDRSPH+0.5*INSDRCYL-(LDDRSPH+0.5*LDDRCYL),
        ERRDRCYLV = sqrt(
            (INSDRCYL*cos(deg2rad(2*INSDRAX))-LDDRCYL*cos(deg2rad(2*LDDRAX)))^2+
            (INSDRCYL*sin(deg2rad(2*INSDRAX))-LDDRCYL*sin(deg2rad(2*LDDRAX)))^2
        )
    ) %>% 
    filter(
        !is.na(INSAV) & abs(INSAV) <= 0.5,
        !is.na(INSGMC) & abs(INSGMC) <= 1,
        !is.na(ERRDRCYLV) & abs(ERRDRCYLV) <= 0.5
    )

geom_bar_cnt(lens_pr_noerr, "DBPVALID")

```


```{r}
lens_pr_noerr_dbpvalid <- lens_pr_noerr %>% 
    filter(DBPVALID == TRUE)
```

See the appendix for a list of the jobs with unsucessful DBP.

### 3.3 DBP values

Percentage of DBP values in interval [-2,2] for x and y and [-5,5] for $\theta$.

```{r}
lens_pr_noerr_dbpvalid %>% 
    filter(DBPVALID == TRUE) %>% 
    mutate(
        DBPINLIMIT = abs(DBPX) <= 2 && abs(DBPY) <= 2 && abs(DBPT) <= 5,
        DBPINLIMIT = fct_recode(as.factor(DBPINLIMIT), DBP_VAL_IN_LIM = "TRUE", DBP_VAL_OUT_LIM = "FALSE") 
    ) %>% 
    geom_bar_cnt("DBPINLIMIT")
```


```{r DBP X, Y and T plots}
lens_pr_noerr_dbpvalid %>% 
    select(DBPX, DBPY, DBPT) %>% 
    gather(NAME, VALUE) %>% 
    mutate(NAME = factor(NAME, levels = c("DBPX", "DBPY", "DBPT"))) %>% 
    ggplot(aes(VALUE)) +
    geom_histogram(bins = 50, aes(fill = NAME), color = "black", alpha = 1) +
    scale_x_symmetric(lim = c(-3,3))+
    facet_wrap(~ NAME)+
    guides(fill = FALSE)+
    labs(
        x = "",
        y = "",
        title = "DBP values"
    )
```

#### More info on the DBP X distribution in two groups

Two groups :

```{r}
lens_pr_noerr_dbpvalid %>% 
    mutate(HIGHDBPX = DBPX > 0.5) %>% 
    ggplot(aes(DBPX, fill = HIGHDBPX)) +
    geom_histogram(color = "black", bins = 100) +
    scale_x_continuous(lim = c(-3,3), breaks = seq(-3,3, by = 0.5)) +
    geom_vline(xintercept = 0.5)+
    labs(
        title = "Two groups for the DBPX values",
        y = "",
        x = "DBPX"
    )
```

#### Link between DBPX and the ENGRAVER

Here are some data linking the DBPX values and the engraver
identifier for about 40 lenses.

```{r}
eng_route <-read_csv("data/eng_routes.csv", 
                     col_types = cols(
                          JOB = col_character(),
                          EYE = col_character(),
                          ENG = col_character(),
                          TIMESTAMP = col_datetime(format = ""),
                          DBPX = col_double(),
                          LDVEN = col_character(),
                          LNAME = col_character(),
                          LTYPE = col_character(),
                          INSGMC = col_double(),
                          INSGMCDBP = col_double()
                        )
                     ) %>% 
    mutate(ENG = as.factor(ENG))

eng_route %>% 
    ggplot(aes(DBPX, fill = ENG)) + 
    geom_histogram(bins = 50, color = "black") +
    geom_vline(xintercept = 0.5, alpha = .5) +
    scale_x_continuous(breaks = seq(-3, 3, by = 0.5), limits = c(-3,3)) +
    labs(
        title = "The two groups for DBPX are related to the engraver!",
        x = "DBPX", 
        y = ""
    )

```



### 3.4 DBP FE and SE values

These are the two validity criteria for the DBP.
DBPFE represents the average error and DBPSE the sensitivity
against shifting.

```{r DBP FE and SE plots}
lens_pr_noerr_dbpvalid %>% 
    select(DBPFE, DBPSE) %>% 
    gather(NAME, VALUE) %>% 
    ggplot(aes(VALUE)) +
    geom_histogram(bins = 30, aes(fill = NAME), color = "black", alpha = 1)+
    facet_wrap(~ NAME) +
    guides(fill = FALSE) +
    labs(
        x = "",
        y = ""
    )
```

## 4. Errors statistics with DBP OFF and ON

### 4.1 Relative prism error with DBP OFF and ON

Here are the relative error on the prismatic powers. 
These errors are the differences between the measured values and the verification values divided by the tolerance values
compliant with the ISO8980-2. The values with and without DBP are compared.

```{r rel prism errors}
lens_pr_noerr_dbpvalid %>% 
    select(REL_DPRVH:REL_DPRVV_DBP) %>% 
    gather(NAME, VALUE,REL_DPRVH:REL_DPRVV_DBP) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "_DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    geom_histogram(bins = 50, aes(fill = NAME), color = "black", alpha = 1)+
    facet_grid(DBP ~ NAME) +
    guides(fill = FALSE) +
    scale_x_symmetric(lim = c(-2,2), labels = percent)+
    labs(
        x = "Relative prismatic error [%]",
        y = ""
    )
```

Here's a comparison of lenses within tolerance (based on a quick evaluation, and
assuming the ISO8980-2 is applied) and out of tolerance for horizontal and vertical prism before and after DBP.

Note that the DBP would not be applied if a lens was considered out of tolerance 
when applying it.


```{r}
lens_pr_noerr_dbpvalid %>% 
    filter(!is.na(REL_DPRVH)) %>% 
    mutate(
        PRVH_OUT = abs(REL_DPRVH) > 1,
        PRVHDBP_OUT = abs(REL_DPRVH_DBP) > 1
        ) %>% 
    count(PRVH_OUT, PRVHDBP_OUT) %>% 
    mutate(percents = n/sum(n)*100) %>% 
    kable(digits = 1)
```

```{r}
lens_pr_noerr_dbpvalid %>% 
    filter(!is.na(REL_DPRVV)) %>% 
    mutate(
        PRVV_OUT = abs(REL_DPRVV) > 1,
        PRVVDBP_OUT = abs(REL_DPRVV_DBP) > 1
        ) %>% 
    count(PRVV_OUT, PRVVDBP_OUT) %>% 
    mutate(percents = n/sum(n)*100) %>% 
    kable(digits = 1)
```


### 4.2 Vector cylinder power errors with DBP OFF and ON

```{r cylv errors}
lens_pr_noerr_dbpvalid %>% 
    mutate(
        DAX = -DBPT,
        INSDRAX_DBP = INSDRAX-DAX,
        DCYLV = cylv_diff(INSDRCYL, INSDRAX, LDDRCYL, LDDRAX),
        DCYLV_DBP = cylv_diff(INSDRCYL, INSDRAX_DBP, LDDRCYL, LDDRAX)
    ) %>% 
    select(DCYLV, DCYLV_DBP) %>% 
    gather(NAME, VALUE) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "_DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    #geom_freqpoly(bins = 50, aes(color = DBP)) +
    geom_histogram(bins = 50, aes(fill = DBP), color = "black", alpha = 1)+
    facet_wrap(~DBP) +
    guides(fill = FALSE) +
    scale_x_continuous(lim = c(0,0.35))+
    labs(
        x = "CYLV errors [D]",
        y = ""
    )
    
```

Here's a comparison of lenses within tolerance (based on a quick evaluation and a tolerance of 0.12D on the cylinder error as a vector, i.e. including cylinder axis) for cylinder and cylinder axis before and after DBP.

```{r}
lens_pr_noerr_dbpvalid %>% 
    mutate(
        DAX = -DBPT,
        INSDRAX_DBP = INSDRAX-DAX,
        DCYLV = cylv_diff(INSDRCYL, INSDRAX, LDDRCYL, LDDRAX),
        DCYLV_DBP = cylv_diff(INSDRCYL, INSDRAX_DBP, LDDRCYL, LDDRAX)
    ) %>% 
    mutate(
        DCYLV_OUT = abs(DCYLV) > 0.12,
        DCYLV_DBP_OUT = abs(DCYLV_DBP) > 0.12
        ) %>% 
    count(DCYLV_OUT, DCYLV_DBP_OUT) %>% 
    mutate(percents = n/sum(n)*100) %>% 
    kable(digits = 1)
```



### 4.3 GMC statistics with DBP OFF and ON

```{r INSGMC}
lens_pr_noerr_dbpvalid %>% 
    select(INSGMC, INSGMCDBP) %>% 
    gather(NAME, VALUE) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    #geom_freqpoly(bins = 50, aes(color = DBP)) +
    geom_histogram(bins = 30, aes(fill = DBP), color = "black", alpha = 1)+
    guides(fill = FALSE) +
    facet_wrap(~ DBP) +
    scale_x_continuous(lim = c(0,0.5))+
    labs(
        x = "INSGMC",
        y = ""
    )
```

Here's a comparison of lenses within tolerance for GMC
if the tolerance was fixed at 0.12.

```{r}
lens_pr_noerr_dbpvalid %>% 
    mutate(
        INGMC_OUT = abs(INSGMC) > 0.12,
        INSGMCDBP_OUT = abs(INSGMCDBP) > 0.12
        ) %>% 
    count(INGMC_OUT, INSGMCDBP_OUT) %>% 
    mutate(percents = n/sum(n)*100) %>% 
    kable(digits = 1)
```

### 4.4 AV statistics with DBP OFF and ON

```{r}
lens_pr_noerr_dbpvalid %>% 
    select(INSAV, INSAVDBP) %>% 
    gather(NAME, VALUE) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    #geom_freqpoly(bins = 50, aes(color = DBP)) +
    geom_histogram(bins = 30, aes(fill = DBP), color = "black", alpha = 1)+
    facet_wrap(~DBP) +
    guides(fill = FALSE) +
    scale_x_continuous(lim = c(0,0.25))+
    labs(
        x = "INSAV [D]",
        y = ""
    )
```


## Appendix

### Unsucessfull DBP jobs


```{r}
lens_pr_noerr %>%
    filter(DBPVALID == FALSE) %>% 
    mutate(TIMESTAMP = date(TIMESTAMP)) %>% 
    select(TIMESTAMP, JOB, EYE, DBPVALID, INSGMC, INSAV, ERRDRSEQ, ERRDRCYLV, LMERRCODE, LNAME) %>%
    arrange(desc(abs(INSAV), INSGMC)) %>% 
    kable()
```