---
output: html_document
editor_options: 
  chunk_output_type: console
params:
    name : "2018-11-20"
title : "DBP stats for `r params$name`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(scales)
library(lemon)
library(knitr)
theme_set(theme_light())
source("dbp_stat_functions.R")
```

```{r lens, include = FALSE}
lens <- read_delim(str_c("../data/",params$name, ".csv"), delim = ";") %>% 
    mutate(
        LMMEASDONE = parse_logical(LMMEASDONE),
        POS34VALID = parse_logical(POS34VALID),
        POSPEVALID = parse_logical(POSPEVALID),
        POLAR = parse_logical(POLAR),
        DBPVALID = parse_logical(DBPVALID),
        TOLVPRVH = get_tolvprvh(LDDRSPH, LDDRCYL),
        TOLVPRVV = get_tolvprvv(LDDRSPH, LDDRCYL)
        )
```

## 1. Data processing and lens statistics

```{r lens_filter1}
lens_filter1 <- lens %>% 
    filter(
        str_detect(LTYPE, "PR"),
        #ENGLOC== "B",
        LMMEASDONE == TRUE
    ) %>% 
    mutate(
        POSPEID = factor(POSPEID),
        POSPEID = fct_recode(POSPEID, 
                             AutoPosPE = "0", 
                             SquareNotFound = "20060", 
                             EyeNotFound  = "20217"
                             )
    )
            
```

The applied filter selects the rows that are compliant with the following conditions :

* LTYPE includes PR
* ENGLOC==B > not enabled since ENGLOC is set to TRUE for some reason
* DLM TResult Measurement done flag is at TRUE 

The total number of lenses included is : `r lens_filter1 %>% nrow`.

Some basic statistics :

```{r lens statistics}
lens_filter1 %>% 
    mutate(
        LDDRSEQ = LDDRSPH + LDDRCYL/2,
        LDDRCYL = abs(LDDRCYL)
        ) %>% 
    select(LDDRSEQ, LDDRCYL, LDADD) %>% 
    gather(NAME, VALUE) %>% 
    mutate(NAME = factor(NAME, levels = c("LDDRSEQ", "LDDRCYL", "LDADD"))) %>% 
    ggplot(aes(VALUE)) +
    geom_histogram(bins = 20, aes(fill = NAME), color = "black", alpha = 1) +
    facet_wrap(~ NAME, scales = "free")+
    guides(fill = FALSE)+
    labs(
        x = "[D]",
        y = "",
        title = ""
    )
    
```


## 2. Preliminary engravings detection and position 

### 2.1 PE Automatic detection rate

```{r}
geom_bar_cnt(lens_filter1, "POSPEID")
```


### 2.2 Preliminary engraving position vs. expected


Here the comparison of the position of the PRP based on the engravings at 34mm
and the PRP based on the preliminary engravings.


```{r lens_auto}
lens_auto <- lens_filter1 %>% 
   filter(POSPEID == "AutoPosPE")
```


```{r PrpDelta_plot}
lens_auto %>% 
    mutate(
       fcocx = FCOCIN * ((EYE=="R")-(EYE=="L")),
       fcocy = FCOCUP,
       PrpDeltaX = POSPEX + TPERRPEX + fcocx - (POS34X + TPERR34X),
       PrpDeltaY = POSPEY + TPERRPEY + fcocy - (POS34Y + TPERR34Y),
       PrpDeltaT = ((POSPET + TPERRPET)-(POS34T+TPERR34T))%%180.0-90
       ) %>%
    select(PrpDeltaX, PrpDeltaY, PrpDeltaT) %>%
    gather(Name, Value) %>% 
    mutate(Name = factor(Name, levels = c("PrpDeltaX", "PrpDeltaY", "PrpDeltaT"))) %>% 
    ggplot(aes(Value))+
    geom_histogram(bins = 20, color = "black", aes(fill = Name), alpha = 1) +
    scale_x_symmetric(lim = c(-1.,1.))+
    guides(fill = FALSE)+
    facet_wrap(~ Name) +
    labs(
        x = "",
        y = "",
        title = "Error on PE position"
    )
```

## 3. DBP success rate and output

### 3.1 DBP success rate
Here is the percentage of successful DBP processing.

```{r DBP_success_rate_plot}
lens_auto %>% 
    mutate(
        DBPVALID = fct_recode(as.factor(DBPVALID), DBP_VALID = "TRUE", DBP_NOT_VALID = "FALSE")
        ) %>% 
    geom_bar_cnt("DBPVALID")
```

See the appendix for a list of the jobs with unsucessful DBP.

### 3.2 DBP values

Percentage of DBP values in interval [-2,2] for x and y and [-5,5] for $\theta$.

```{r}
lens_auto %>% 
    filter(DBPVALID == TRUE) %>% 
    mutate(
        DBPINLIMIT = abs(DBPX) <= 2 && abs(DBPY) <= 2 && abs(DBPT) <= 5,
        DBPINLIMIT = fct_recode(as.factor(DBPINLIMIT), DBP_VAL_IN_LIM = "TRUE", DBP_VAL_OUT_LIM = "FALSE") 
    ) %>% 
    geom_bar_cnt("DBPINLIMIT")
```


```{r DBP X, Y and T plots}
lens_auto %>% 
    filter(DBPVALID == TRUE) %>% 
    select(DBPX, DBPY, DBPT) %>% 
    gather(NAME, VALUE) %>% 
    mutate(NAME = factor(NAME, levels = c("DBPX", "DBPY", "DBPT"))) %>% 
    ggplot(aes(VALUE)) +
    geom_histogram(bins = 20, aes(fill = NAME), color = "black", alpha = 1) +
    scale_x_symmetric(lim = c(-3,3))+
    facet_wrap(~ NAME)+
    guides(fill = FALSE)+
    labs(
        x = "",
        y = "",
        title = "DBP values"
    )
```

### 3.3 DBP FE and SE values

These are the two validity criteria for the DBP.
DBPFE represents the average error and DBPSE the sensitivity
against shifting.

```{r DBP FE and SE plots}
lens_auto %>% 
    filter(DBPVALID == TRUE) %>% 
    select(DBPFE, DBPSE) %>% 
    gather(NAME, VALUE) %>% 
    ggplot(aes(VALUE)) +
    geom_histogram(bins = 30, aes(fill = NAME), color = "black", alpha = 1)+
    facet_wrap(~ NAME) +
    guides(fill = FALSE) +
    labs(
        x = "",
        y = ""
    )
```

## 4. Errors statistics with DBP OFF and ON

### 4.1 Relative prism error with DBP OFF and ON

Here are the relative error on the prismatic powers. 
This errors are the difference between the measured values and the verifications value divided by the tolerance
compliant with the ISO8980-2. The values with and without DBP are compared.

```{r rel prism errors}
lens_auto %>% 
    mutate(
        INSPRVH_DBP = extrapolate_prvh(INSPRVH, INSPRVV, INSPRSPH, INSPRCYL, INSPRAX,
                                        -DBPX, -DBPY, -DBPT),
        INSPRVV_DBP = extrapolate_prvv(INSPRVH, INSPRVV, INSPRSPH, INSPRCYL, INSPRAX,
                                        -DBPX, -DBPY, -DBPT),
        REL_DPRVH = (INSPRVH-LDPRVH)/TOLVPRVH,
        REL_DPRVV = (INSPRVV-LDPRVV)/TOLVPRVV,
        REL_DPRVH_DBP = (INSPRVH_DBP - LDPRVH)/TOLVPRVH,
        REL_DPRVV_DBP = (INSPRVV_DBP - LDPRVV)/TOLVPRVV
        ) %>% 
    select(REL_DPRVH:REL_DPRVV_DBP) %>% 
    gather(NAME, VALUE) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "_DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    geom_histogram(bins = 50, aes(fill = NAME), color = "black", alpha = 1)+
    facet_grid(DBP ~ NAME) +
    guides(fill = FALSE) +
    scale_x_symmetric(lim = c(-1,1), labels = percent)+
    labs(
        x = "Relative prismatic error [%]",
        y = ""
    )
```

### 4.2 Vector cylinder power errors with DBP OFF and ON

```{r cylv errors}
lens_auto %>% 
    mutate(
        DAX = -DBPT,
        INSDRAX_DBP = INSDRAX-DAX,
        DCYLV = cylv_diff(INSDRCYL, INSDRAX, LDDRCYL, LDDRAX),
        DCYLV_DBP = cylv_diff(INSDRCYL, INSDRAX_DBP, LDDRCYL, LDDRAX)
    ) %>% 
    select(DCYLV, DCYLV_DBP) %>% 
    gather(NAME, VALUE) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "_DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    #geom_freqpoly(bins = 50, aes(color = DBP)) +
    geom_histogram(bins = 30, aes(fill = DBP), color = "black", alpha = 1)+
    facet_wrap(~DBP) +
    guides(fill = FALSE) +
    scale_x_continuous(lim = c(0,0.25))+
    labs(
        x = "CYLV errors [D]",
        y = ""
    )
    
```

### 4.3 GMC statistics with DBP OFF and ON

```{r INSGMC}
lens_auto %>% 
    select(INSGMC, INSGMCDBP) %>% 
    gather(NAME, VALUE) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    #geom_freqpoly(bins = 50, aes(color = DBP)) +
    geom_histogram(bins = 30, aes(fill = DBP), color = "black", alpha = 1)+
    guides(fill = FALSE) +
    facet_wrap(~ DBP) +
    scale_x_continuous(lim = c(0,0.5))+
    labs(
        x = "INSGMC",
        y = ""
    )
```

### 4.4 AV statistics with DBP OFF and ON

```{r}
lens_auto %>% 
    select(INSAV, INSAVDBP) %>% 
    gather(NAME, VALUE) %>% 
    mutate(
        DBP = str_detect(NAME, "DBP"),
        DBP = fct_recode(as.factor(DBP), DPB_OFF = "FALSE", DBP_ON = "TRUE"),
        NAME = str_replace(NAME, "DBP", "")
        ) %>% 
    ggplot(aes(VALUE)) + 
    #geom_freqpoly(bins = 50, aes(color = DBP)) +
    geom_histogram(bins = 30, aes(fill = DBP), color = "black", alpha = 1)+
    facet_wrap(~DBP) +
    guides(fill = FALSE) +
    scale_x_continuous(lim = c(0,0.25))+
    labs(
        x = "INSAV [D]",
        y = ""
    )
```


## Appendix

### Unsucessfull DBP jobs

```{r}
lens_auto %>% 
    filter(DBPVALID == FALSE) %>% 
    select(JOB, EYE, DBPVALID) %>% 
    kable()
```









